Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-19 U_v16.tex
Test pour voir
Constantes_1D
Explicitation des constantes jusqu'à p12 incluse

\begin{hyp}[Regularity of the mesh in 1D] \label{geometrie1d}
 We consider there exists 
a universal constant $C>0$ independent of the mesh size
$h=\sup_{j\in \mathbb Z} \Delta x_j $
so that one has 
$$
Ch \leq \Delta x_j \leq h \qquad \forall j \in \mathbb{Z}.
$$
\end{hyp}

@@

Our goal is this section is to show that this scheme is AP.

When $\eps$ tends to $0$, 
 the scheme $P_h^\eps$ admits the 
diffusion limit scheme $P_h^0$
\begin{equation}\label{schemadifff}
P_h^0: \qquad
\displaystyle\Delta x_j\frac{d}{dt} p_j -\frac{1}{\sigma } \bigg(
\frac{p_{j+1}-p_j}{\Delta x_{j+\frac12 }}-\frac{p_j -p_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0
\end{equation}

The natural cellwise initialization is
\begin{equation} \label{eq:intip0}
p_j(0)=p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Other quantities are 
\begin{equation} \label{eq:vv}
\left \{
\begin{array}{l}
\displaystyle v_{j+\frac12 }=-\frac{1}{\sigma}\frac{p_{j+1}-p_{j}}{\Delta
x_{j+\frac12 }},\\
\displaystyle v_j=\frac{v_{j+\frac12 }+v_{j-\frac12 }}{2}.
\end{array}
\right.
\end{equation}

Provided that the initial data is smooth, the initialization gives us 
\begin{equation}\label{init_1D}
 \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C h\eps .
\end{equation}

We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
u^{\eps}(x_j,t)\right)_{j\in \mathbb Z}$ the interpolation of the 
solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left(p_j^{\eps}(t), u_j^{\eps}(t)   \right)_{j\in \mathbb Z}$ the
solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t)=\left(p(x_j,t),\varepsilon v(x_j,t)\right)_{j\in \mathbb Z}$ 
which is the interpolation of the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)=\left( p_j(t),  
\varepsilon v_j(t)   \right)_{j\in \mathbb Z}$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

\begin{proposition} \label{heqtode}
There exists a constant $C>0$ such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
C \eps  \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $u^{\eps}=-\frac{\varepsilon}\sigma \partial_x p^{\eps}$ and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p^{\eps} +\frac{1}{\eps}\partial_{x}u^{\eps}=0,\\
\partial_t u^{\eps} + \frac{1}{\eps}\partial_x p^{\eps} +\frac{\sigma}{\eps^2}u^{\eps} = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt u^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p^{\eps}=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p^{\eps}$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=u-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{array}{lll}
\displaystyle\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
\displaystyle\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
\displaystyle 
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps}

=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{array}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

In this section we  
prove the 
convergence of $P_h^\varepsilon $ to  $P^\varepsilon $. We still denote $V^\eps(t)=(p^\eps,u^\eps)$.
\begin{proposition}\label{cv1d}
There exist a constant $C(T)>0$ independent of $\eps$ and $h$ 
 such that the following estimate holds 
\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) 
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

For the sake of simplicity,for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $. One has 

@@

 D_3 = \sum_{j\in \mathbb{Z}}

@@

\hspace{0.8cm}+\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}

@@

 D_3 &=& \underset{j\in \mathbb{Z}}{\sum}

@@

& +& \underset{j\in \mathbb{Z}}{\sum}

@@

&-&\underset{j\in \mathbb{Z}}{\sum} 

@@

p^{\eps}_j

@@

&+& \underset{j\in \mathbb{Z}}{\sum} \Delta x_j  \frac{\sigma}{\eps^2}

@@

 D_3 &\leq& \alpha \sum_{j\in \mathbb{Z}}

@@

&+&\sum_{j\in \mathbb{Z}} \bigg(

@@

&+& \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2

@@

&-& \sum_{j\in \mathbb{Z}} u^{\eps}_j 

@@

@@

\mathscr{E}'(t)  & \leq & (-1+\alpha) \sum_{j\in \mathbb{Z}}

@@

&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}

@@

&+& \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2} u^{\eps}_j \:

@@

we obtain

@@

\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$
\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1} ) and (\ref{bee2} ), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and estimate \eqref{estiuepsflux}, one can find a constant $C\geq0$ such that the next term can be  bounded like 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq C h \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent so 
 $\mathscr{E}(0)\leq Ch^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme, assuming smooth initial data.
\eqref{schemadifff}. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

\sigma^{-1}\sum_j \Delta x_j s_j e_j+\sigma^{-1}\sum_jr_{j+\frac12 }(e_j-e_{j+1}).

@@

\sigma^{-1}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
\frac12 \|r_h\|^2_{L^2(\mathbb{R})}.
Using the  definitions of  the truncation errors $s_h$ and $r_h$, these
quantites can be   
bounded independently of the time of observation $T$ 

@@

\|r_h\|_{L^2([0,T]\times\mathbb{R})}  \leq C h \bigg(
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}+\|\partial_{xx}p_0\| _{L^2(\mathbb{R})} \bigg).

@@

\| \widehat s_h\|_{L^2(\mathbb{R})} \|\widehat e_h\|_{L^2(\mathbb{R})}+

@@

\frac12
\left(\| \widehat s_h\|_{L^2(\mathbb{R})}^2+ \frac{1}{\sigma} \|\widehat r_h\|^2_{L^2(\mathbb{R})}  \right)+\frac12 
 \|\widehat e_h\|^2_{L^2(\mathbb{R})}

@@

\| e_h\|_{L^\infty([0,T];\mathbb{R})}\leq C(T) h 

@@

 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).

@@

f_h=\eps\left(v(x_j)-v_j    \right)_{j\in \mathbb Z}=-\eps

>>>>

\begin{hyp}[Regularity of the mesh in 1D] \label{geometrie1d}
 We consider that there exists 
a universal constant $C_{\mathcal{M}}>0$ independent of the mesh size
$h=\sup_{j\in \mathbb Z} \Delta x_j $
so that one has 
$$
C_{\mathcal{M}} h \leq \Delta x_j \leq h \qquad \forall j \in \mathbb{Z}.
$$
\end{hyp}

@@

Our goal is this section is to show that this scheme is AP. When $\eps$ tends to $0$, 
 the scheme $P_h^\eps$ admits the 
diffusion limit scheme $P_h^0$
\begin{equation}\label{schemadifff}
P_h^0: \qquad
\displaystyle\Delta x_j\frac{d}{dt} p_j -\frac{1}{\sigma } \bigg(
\frac{p_{j+1}-p_j}{\Delta x_{j+\frac12 }}-\frac{p_j -p_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0
The natural cellwise initialization is
\begin{equation} \label{eq:intip0}
p_j(0)=p_0(x_j) \mbox{ for all }j\in \mathbb Z.
Other quantities are 
\begin{equation} \label{eq:vv}
\left \{
\displaystyle v_{j+\frac12 }=-\frac{1}{\sigma}\frac{p_{j+1}-p_{j}}{\Delta
x_{j+\frac12 }},\\
\displaystyle v_j=\frac{v_{j+\frac12 }+v_{j-\frac12 }}{2}.
Provided that the initial data is smooth, the initialization gives us 
\begin{equation}\label{init_1D}
 \| u_j^{\eps}(0)-\eps v_j(0)\|_{L^2(\mathbb{R})} \leq C h\eps .
We denote by $\V^{\eps}(t)=\left(p^{\eps}(x_j,t),
u^{\eps}(x_j,t)\right)_{j\in \mathbb Z}$ the interpolation of the 
solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left(p_j^{\eps}(t), u_j^{\eps}(t)   \right)_{j\in \mathbb Z}$ the
solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t)=\left(p(x_j,t),\varepsilon v(x_j,t)\right)_{j\in \mathbb Z}$ 
which is the interpolation of the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)=\left( p_j(t),  
\varepsilon v_j(t)   \right)_{j\in \mathbb Z}$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

\begin{proposition} \label{heqtode}
There exists a constant $C>0$ such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
 \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $\widehat{u}^{\eps}=-\frac{\varepsilon}\sigma \partial_x p$, where $p$ is the solution of the diffusion equation\eqref{difffff} and we
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p +\frac{1}{\eps}\partial_{x}\widehat{u}^{\eps}=0,\\
\partial_t \widehat{u}^{\eps} + \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}\widehat{u}^{\eps} = R^{\eps},
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt \widehat{u}^{\eps}=-\frac{\varepsilon}\sigma \partial_{tx} p =
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=\widehat{u}^{\eps}-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{aligned}
&\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
&\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
&
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps} 
=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{aligned}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

In this section we  
prove the 
convergence of $P_h^\varepsilon $ to  $P^\varepsilon $. We still denote $V^\eps(t)=(p^\eps,u^\eps)$.
\begin{proposition}\label{cv1d}
Under assumption \ref{geometrie1d} on the mesh and assuming that the initial conditions satisfy \eqref{eq:initp1}, the following estimate holds 
\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

For the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $. One has 

@@

 D_3 &= \sum_{j\in \mathbb{Z}}

@@

&+\sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}

@@

 D_3 &= \underset{j\in \mathbb{Z}}{\sum}

@@

& + \underset{j\in \mathbb{Z}}{\sum}

@@

&-\underset{j\in \mathbb{Z}}{\sum} 

@@

p^{\eps}_j -

@@

&+ \underset{j\in \mathbb{Z}}{\sum} \Delta x_j  \frac{\sigma}{\eps^2}

@@

 D_3 &\leq \alpha \sum_{j\in \mathbb{Z}}

@@

&+\sum_{j\in \mathbb{Z}} \bigg(

@@

&+ \sum_{j\in \mathbb{Z}} \frac{1}{8\eps} \sigma \Delta x_j^2

@@

&- \sum_{j\in \mathbb{Z}} u^{\eps}_j 

@@

\frac{u^{\eps}(x_{j+\frac12 })-u^{\eps}(x_{j-\frac12 })}{\eps}.

@@

\mathscr{E}'(t)  & \leq (-1+\alpha) \sum_{j\in \mathbb{Z}}

@@

&+ \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2}

@@

&+ \sum_{j\in \mathbb{Z}} \Delta x_j  \frac{\sigma}{\eps^2} u^{\eps}_j \:

@@

@@

\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R)) }.
Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2(\mathbb R) }
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\frac{\sigma^2}{4\eps^3}
h \|  \mathbf u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+\frac{1}{4C_{\mathcal{M}}}+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})} .

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

\frac{1}{\sigma}\sum_j \Delta x_j s_j e_j+\frac{1}{\sigma}\sum_jr_{j+\frac12 }(e_j-e_{j+1}).

@@

\frac{1}{\sigma}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
\frac{1}{2\sigma} \|r_h\|^2_{L^2(\mathbb{R})}.
Using the  definitions of  the truncation error $s_h$, one easilly obtains by using classical arguments $\|s_h\|_{L^2([0,T]\times\mathbb{R})}\leq \sqrt{2}h\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})}$. Since $p$ satisfies the diffusion equation \eqref{difffff}, one gets $\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma/2} \|\partial_{xx}p_0\|_{L^2(\mathbb{R})}$. The same manipulations on the second truncation error $r_h$ yields

@@

\|r_h\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma} h \bigg(
 \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})} +\|\partial_{x}p_0\| _{L^2(\mathbb{R})} \bigg).

@@

\frac{1}{\sigma} \| \widehat s_h\|_{L^2(\mathbb{R})} \|\widehat e_h\|_{L^2(\mathbb{R})}+

@@

\frac{1}{2\sigma}
\left(\| \widehat s_h\|_{L^2(\mathbb{R})}^2+  \|\widehat r_h\|^2_{L^2(\mathbb{R})}  \right)+ \frac{1}{2\sigma}
 \|\widehat e_h\|^2_{L^2(\mathbb{R})},

@@

\| e_h\|_{L^\infty([0,T];L^2(\mathbb{R}))}\leq h 

@@

 \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}
\right)e^{T/2\sigma}.

@@

f_h=\eps\left(v(x_j)-v_j    \right)_{j\in \mathbb Z}= - \eps
